Multidimensional signals and analytic flexibility: Estimating degrees of freedom in human speech analyses

### 2023-01-13 RR_manuscript/Draft_RR.Rmd
add acknowledgements and funding info

>>>>

# Acknowledgements

We would like to thank the editors David Sbarra and Julia Strand, Matthew Goldrick and two anonymous reviewers for their insightful comments and suggestions.

The initiating authors (SC, JVC, TR) wish to express immense gratitude to all the other authors, without which this project would not have come to be.

All remaining errors are the initiating authors' (SC, JVC, TR)

# Funding

Stefano Coretta was partially supported by the European Research Council Grant No. 742289 Human interaction and the evolution of spoken accent (2017–2022) awarded to Prof. Jonathan Harrington.

Jalal Al-Tamimi was partially supported by the French Investissements d'Avenir - Labex EFL program (ANR-10- LABX-0083), contributing to the IdEx Université Paris Cité - ANR-18-IDEX-0001.

George Moroz, Sita Carraturo: The research leading to these results has received funding from the Basic Research Program at the National Research University Higher School of Economics.

Iñigo	Urrestarazu-Porta: The research leading to these results has received funding from the MADPAB (National Research Agency of the French republic, ANR-20-CE27-0007) and Monumenta Linguae Vasconum 6: avances en la cronología de la historia y la prehistoria de la lengua vasca projects (Ministry of Science and Innovation of the Spanish kingdom, PID2020-118445GB-I00).

Constantijn	Kaland, Martine Grice: German Research Foundation (DFG) - Project-ID 281511265 - SFB 125.

Nina R. Benway: This research was supported in part through computational resources provided by Syracuse University (NSF ACI-1341006; NSF ACI-1541396).
